Draft - Enhancing Forecast Reconciliation: A Study of Covariance Estimation

### 2025-04-28 literature/paper_draft.Rmd
small fixes in notation

Hierarchical/Grouped time series satisfy a set of linear constraints, often represented as: $$
y_t = S b_t,
$$ where $S$ is a summing matrix of order $m x n$ which aggregates the bottom-level series $b_t$ ($n$-vector) to the series at aggregation levels above. The $m$-vector $y_t$ contains all observations at time $t$

>>>>

Hierarchical/Grouped time series satisfy a set of linear constraints, often represented as: 
$$
\bm{y}_t = \bm{S} \bm{b}_t,
$$ 
where $\bm{S}$ is a summing matrix of order $m x n$ which aggregates the bottom-level series $\bm{b}_t$ ($n$-vector) to the series at aggregation levels above. The $m$-vector $\bm{y}_t$ contains all observations at time $t$
